---
title: "Plotly"
author: "Hyun Jin Jung"
date: "2023-10-30"
output: html_document
---

```{r, include = FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)

data("rest_inspec")
```

We will be using `NYC Restaurant Inspections` dataset to make plots.

```{r}
tidy_rest_inspec = rest_inspec |>
  filter(grade %in% c("A", "B", "C"), boro != "Missing") |>
  mutate(boro = str_to_title(boro),
         dba = str_to_upper(dba)) |>
  mutate(cuisine_description = recode(
    cuisine_description,
    "Latin (Cuban, Dominican, Puerto Rican, South & Central American)" = "Latin",
    "Bottled beverages, including water, sodas, juices, etc." = "Bottled Beverages"
  )) |>
  select(boro, critical_flag, cuisine_description, dba, score, violation_code, zipcode, grade)
```
Renamed "Latin (Cuban, Dominican, Puerto Rican, South & Central American)" to "Latin" and "Bottled beverages, including water, sodas, juices, etc." to "Bottled Beverages", to improve plot aesthetics and space utilization.

### Distribution of Scores for Grade "C" Restaurants by Cuisine Description and Borough
```{r}
tidy_rest_inspec |>
  filter(grade == "C") |>
  mutate(cuisine_description = fct_reorder(cuisine_description, score)) |>
  plot_ly(x = ~cuisine_description, y = ~score, color = ~boro, type = "box", 
          width = 800, height = 400, colors = "viridis") |>
  layout(yaxis = list(title = "Score"),
         xaxis = list(title = "Cuisine Description",
                      tickfont = list(size = 8)))
```
We filtered the data to focus on restaurants with a "C" grade. Then, we used the `cuisine_description` variable to create a box plot, where each `cuisine_description` is shown on the x-axis and `score` on the y-axis. The data points are colored by `boro`. This visualization provides insights into the distribution of scores for restaurants with a "C" grade based on their `cuisine_descriptions`.

### Relationship Between Cuisine Descriptions, Scores, and Boroughs
```{r}
tidy_rest_inspec |>
  mutate(text_label = str_c("Grade:", grade, "\nCritical Flag:", critical_flag)) |>
  plot_ly(
    x = ~ cuisine_description, y = ~score, type = "scatter", mode = "markers", 
    colors = "viridis", width = 800, height = 400,
    color = ~boro, text = ~text_label, alpha = 0.05) |>
    layout(yaxis = list(title = "Score"),
         xaxis = list(title = "Cuisine Description",
                      tickfont = list(size = 8)))
```
We added a text label for each data point, containing the `Grade` and `Critical Flag` information. Then, we created a scatter plot, with `cuisine_descriptions` on the x-axis and `scores` on the y-axis. The data points are colored by `boro`, and we included the text labels for additional context. This scatter plot visualizes the relationships between `cuisine_descriptions`, `scores`, and `boro`, helping us identify patterns and trends.

### Unique Restaurant Counts by Borough and Grade
```{r}
tidy_rest_inspec |>
  distinct(boro, dba, grade) |>
  group_by(boro, grade) |>
  count(grade) |>
  mutate(grade, fct_reorder(grade, n)) |>
  plot_ly(x = ~grade, y = ~n, color = ~boro, type = "bar", colors = "viridis") |>
  layout(yaxis = list(title = "Count of Restaurants"),
         xaxis = list(title = "Grade"))
```
There is multiple data for the same restaurant. We grouped the data by borough and grade, counted the unique restaurants within each category, and visualized the results in a bar plot.